cardinalR: Generating interesting high-dimensional data structures

### 2025-05-15 paper-cardinalR.Rmd
Updated the .bib

The package can be installed from CRAN using

```r
install.packages("cardinalR")
```

and the development version can be installed from GitHub

@@

## Web site

More documentation of the package can be found at the web site [https://jayanilakshika.github.io/cardinalR/](https://jayanilakshika.github.io/cardinalR/).

@@

## Functions

@@

These `R` packages were used for this work: `cli` [@gabor2025], `tibble` [@kirill2023], gtools [@gregory2023], dplyr [@hadley2023], `stats` [@core2025], `tidyr` [@hadley2024], `purrr` [@hadley2025], `mvtnorm` [@alan2009], `geozoo` [@barret2016], and `MASS` [@venables2002]. This article is created using \CRANpkg{knitr} [@yihui2015] and \CRANpkg{rmarkdown} [@yihui2018] in R with the `rjtools::rjournal_article` template.

>>>>

The development version can be installed from GitHub:

@@

<!-- ## Web site -->

<!-- More documentation of the package can be found at the web site [https://jayanilakshika.github.io/cardinalR/](https://jayanilakshika.github.io/cardinalR/). -->

@@

## Usage

@@

These `R` packages were used for this work: `cli` [@gabor2025], `tibble` [@kirill2023], `gtools` [@gregory2023], `dplyr` [@hadley2023], `stats` [@core2025], `tidyr` [@hadley2024], `purrr` [@hadley2025], `mvtnorm` [@alan2009], `geozoo` [@barret2016], and `MASS` [@venables2002]. This article is created using \CRANpkg{knitr} [@yihui2015] and \CRANpkg{rmarkdown} [@yihui2018] in R with the `rjtools::rjournal_article` template.
